%_______________________________________________________________________________
% @brief    LaTeX2e Resume for Jitendra Kotamraju
\documentclass[margin,line]{resume}
\usepackage{hyperref}


%_______________________________________________________________________________
\begin{document}
\name{\Large Jitendra Kotamraju}
\begin{resume}

%_______________________________________________________________________________
% Contact Information
\section{\mysidestyle Contact}

SFO Bay Area, (408) 439 2485, jitsni@gmail.com, \href{https://www.linkedin.com/in/jitendra-kotamraju-70b37b}{www.linkedin.com/in/jitendra-kotamraju}


%_______________________________________________________________________________
% Objective
\section{\mysidestyle Objective}

Seeking a software development position.

%_______________________________________________________________________________
% Education
\section{\mysidestyle Education}

\textbf{Indian Institute of Technology}, Mumbai, India \hfill \textbf{Jul 1992 -- Jan 1994}\\
\textsl{M.S. in Computer Science}


%_______________________________________________________________________________
% Professional Experience
\section{\mysidestyle Professional\\Experience}

    \textbf{Kaazing Corporation}, San Jose, CA \hfill \textbf{Dec 2013 -- present}\\ 
    \textsl{Principal Software Engineer}\\\\
Worked in the development of Gateway, KWIC, K3PO prducts/projects
    \begin{list2}
    \item \href{http://github.com/kaazing/gateway}{Network Gateway} - Modularity, HTTP reverse proxy, WebSocket
    \item \href{http://github.com/kaazing/k3po}{Network driver and testing tool} - Shared memory, HTTP
    \item \href{http://kaazing.com/product-kwic}{Kaazing Websocket Intercloud Connect} - SOCKS
    \end{list2}\vspace{-1.5mm}

    \textbf{Sun Microsystems/Oracle}, Santa Clara, CA \hfill \textbf{Apr 2003 -- Dec 2013}\\ 
    \textsl{Principal Member of Technical Staff}\\\\
Contributed to the Java EE specification and the GlassFish application server implementation. Served as one of the internal architects for Java EE platform.
    \begin{list2}
    \item Specification lead for \href{http://jcp.org/en/jsr/detail?id=353}{JSON Processing} and maintenance lead for \href{http://jcp.org/en/jsr/detail?id=224}{JAX-WS} and \href{http://jcp.org/en/jsr/detail?id=109}{JSR 109} JSRs
    \item Implemented \href{https://jsonp.java.net}{JSON Processing}, \href{https://tyrus.java.net}{WebSocket}, \href{https://jax-ws.java.net}{JAX-WS}/\href{https://metro.java.net}{Metro} web services stack, \href{https://glassfish.java.net}{GlassFish} application server, \href{https://avatar.java.net}{Project Avatar} and various open source projects
    \item Represented Sun in \href{http://www.ws-i.org}{WS-I} Basic Profile working group
    \end{list2}\vspace{-1.5mm}


    \textbf{Tibco/Tibco Finance/Reuters}, Palo Alto, CA  \hfill \textbf{Aug 1998 -- Mar 2003}\\
    \textsl{Technical Specialist, CTO Technology Innovation Group}\\\\
I have worked in CTO group that deals with process and standards, partnerships, technology trends and innovation and in BTG group that enables Reuters customer segments to develop, deliver and support compelling products, targeted to its clients's needs.

    \begin{list2}
    \item Worked on various technologies, built and demonstrated the proof of concepts and also interacted with various industry groups. Some of the technologies are J2ME, Wireless, P2P, VOIP, Security, Web services and Instant Messaging.
    \item Architected Personalized Delivery System (PDS), an enterprise software product of the Internet Finance Platform, that delivers personalized content to a broad range of delivery vehicles. Designed and implemented a scalable, fault-tolerant, stateless load manager that manages, distributes, and balances user profiles among multiple distributed stateful agent instances. It is built on Tibco's messaging infrastructure.
    \end{list2}\vspace{-1.5mm}

    \textbf{Aquas, Inc}, Sunnyvale, CA \hfill \textbf{Oct 1996 -- Jul 1998}\\ 
    \textsl{Sr Software Engineer}\\\\ 
Aquas created many web products to monitor, analyze and manage web sites. Worked as a core developer and involved in system administration and all aspects of building infrastructure at this startup company.
    \begin{list2}
    \item Implemented a website analysis tool that analyzes the web server access log files and produces various reports
    \item Designed and developed a webbot to create a site graph, and an embedded HTTP server
    \end{list2}\vspace{-1.5mm}


    \textbf{HCL Hewlett Packard}, Chennai, India \hfill \textbf{Apr 1994 -- Apr 1996}\\
    \textsl{Software Engineer}\\
    \begin{list2}
    \item Implemented client and server \href{http://www.ietf.org/rfc/rfc2865.txt}{RADIUS} security protocol in a Remote Access Server (RAS) product.
    \item Designed and implemented an email editor with MIME support, mailcap tool, and POP3 client-server in PostMan email product.
    \end{list2}\vspace{-1.5mm}

%_______________________________________________________________________________
\end{resume}
\end{document}


%_______________________________________________________________________________
% EOF
